Convective penetration probably parameterizes convective overshoot

### 2021-07-20 manuscript/ms.tex

\section{MESA implementation}
\label{app:mesa}
Here we describe a first implementation of Eqn.~\ref{eqn:mesa_eqn} in MESA \citep{paxton_etal_2011, paxton_etal_2013, paxton_etal_2015, paxton_etal_2018, paxton_etal_2019}.
We note that this impelementation is likely not universal or robust enough to be used in any stellar model, but it is robust enough to timestep stably and produce the results displayed in Sct.~\ref{sec:solar_model}.
Future work should improve upon this model.

To find the extent of the penetrative region, we override MESA's TODO routine for writing $\justgrad$ and instead have the solver follow these steps:
\begin{enumerate}
\item At each timestep, we find the location of the Schwarzschild convective boundary, $r_s$.
We measure the value of the mixing length $\lambda$ there, and choose a convection zone length scale $\ell_{\rm{CZ}} = \text{min}(\lambda, L_{\rm{CZ}})$, where $L_{\rm{CZ}}$ is the full depth of the Schwarzschild-unstable convective region.
We take the ``CZ'' integrals in Eqn.~\ref{eqn:mesa_eqn} to span radially from the Schwarzschild boundary to a depth $\ell_{\rm{CZ}}$ within the convection zone.
\item We calculate the buoyancy integral $\int_{\rm{CZ}} L_{\rm{conv}} dr$ and the convection zone volume $V_{\rm{CZ}}$.
\item Starting at the Schwarzschild boundary, we iteratively expand the size of the PZ until Eqn.~\ref{eqn:mesa_eqn} is satisfied.
For each radial bin $i$ below the convection zone, we calculate $\int_{\rm{PZ},i}L_{\rm{conv}} dr$ and $V_{\rm{PZ},i}$.
We evaluate the LHS of Eqn.~\ref{eqn:mesa_eqn} using those values.
If LHS $\geq$ RHS, we assume that the radial coordinate of bin $i$ is the boundary of the penetrative region.
\item We enforce $\justgrad \approx \gradad$ in the PZ by doing TODO.
\item We ensure that the transition from the PZ to the RZ is smooth.
Outside of the PZ, we model $\justgrad$ as TODO.
\end{enumerate}

Using this procedure with $f = 0.8$ and $\xi = 1$, and timestepping a solar model to the age of the current Sun ($\sim$ 4.5 Gyr), we find the profile displayed in Sec.~\ref{sec:solar_model}.

>>>>

\section{MESA implementation}
\label{app:mesa}

Our 1D stellar evolution calculations were performed using the Modules for Experiments in Stellar Astrophysics software instrument\citep[MESA]{paxton_etal_2011, paxton_etal_2013, paxton_etal_2015, paxton_etal_2018, paxton_etal_2019}.

\subsection{Input Physics}

The MESA EOS is a blend of the OPAL \citep{Rogers2002}, SCVH
\citep{Saumon1995}, FreeEOS \citep{Irwin2004}, HELM \citep{Timmes2000},
and PC \citep{Potekhin2010} EOSes.

Radiative opacities are primarily from OPAL \citep{Iglesias1993,
Iglesias1996}, with low-temperature data from \citet{Ferguson2005}
and the high-temperature, Compton-scattering dominated regime by
\citet{Buchler1976}.  Electron conduction opacities are from
\citet{Cassisi2007}.

Nuclear reaction rates are from JINA REACLIB \citep{Cyburt2010} plus
additional tabulated weak reaction rates \citet{Fuller1985, Oda1994,
Langanke2000}.  (For MESA versions before 11701): Screening is
included via the prescriptions of \citet{Salpeter1954, Dewitt1973,
Alastuey1978, Itoh1979}.

\subsection{Penetration Implementation}

Here we describe a first implementation of Eqn.~\ref{eqn:mesa_eqn} in MESA.
We note that this impelementation is likely not universal or robust enough to be used in most complex stellar models, but it is robust enough to time-step stably and produce the results displayed in Sct.~\ref{sec:solar_model}.
Future work should improve upon this model.

To find the extent of the penetrative region we write Eqn.~\eqref{eq:mesa_eqn} as
\begin{align}
	(1-f) \int_{\rm CZ} L_{\rm conv} dr = \int_{\rm PZ} \xi f L_{\rm conv,avg,CZ} + L_{\rm conv} dr,
	\label{eq:rwt}
\end{align}
where $L_{\rm conv,avg,CZ}$ is the average of $L_{\rm conv}$ in the convection zone and $L_{\rm conv}$ in the penetrative region is given by
\begin{align}
	L_{\rm conv} = \frac{L_{\rm rad}}{\nabla_r}(\nabla_a - \nabla_r),
\end{align}
which is the excess luminosity carried if the temperature gradient in the radiative zone is adiabatic.

We first integrate the left-hand side of Eqn.~\eqref{eq:rwt} over the convection zone and further use that to evaluate $L_{\rm conv,avg,CZ}$.
Next we integrate the right-hand side of the same away from the convective boundary into the radiative zone until the equation is satisfied.
The point where this integration stops is the edge of the penetrative region.

We then implement convective penetration in stellar evolution with two modifications.
First, we add an extra chemical mixing term in the penetration zone with a scale of $D \approx H_p (L/4\pi r^2 \rho)^{1/3}$, which is roughly the scale of the convective diffusivity.
The precise choice of diffusivity here does not matter, as any plausible scale will be enough to eliminate any composition gradient on evolutionary time-scales.
Secondly, we override the default routine in MESA for determining $\nabla$ and instead have the solver reduce $\nabla_a-\nabla$ by 90 per~cent in the penetrative zone.

Using this procedure with $f = 0.86$ and $\xi = 0.6$, and timestepping a solar model to the age of the current Sun ($\sim$ 4.5 Gyr), we find the profile displayed in Sec.~\ref{sec:solar_model}.

\subsection{Models}

Models were constructed to reasonably reproduce the present-day Sun and based on the 2019 MESA summer school lab by~\citet{pm}.
Inlists and the \texttt{run\_star\_extras} source code are available at CITE.
